\documentclass[a4paper,12pt]{report}

\usepackage[utf8]{inputenc} 
\usepackage[T5]{fontenc}    
\usepackage[vietnamese]{babel}
\usepackage{amsfonts,amsmath,amssymb,amsthm}

\usepackage{float}
\usepackage{geometry}
\geometry{left=3cm,right=2cm,top=2.5cm,bottom=2.5cm}
\usepackage{indentfirst}

\usepackage{fancyhdr}
\usepackage{hyperref} 
\usepackage{graphicx}
\usepackage{eso-pic}
\usepackage{url}

\title{Báo cáo Tốt nghiệp}
\author{Bùi Minh Thành}
\date{2024}

\begin{document}

\input{01_title}

\input{02_thanks} % Lời cảm ơn

\tableofcontents % Mục lục

\input{03_word} % Danh mục thuật ngữ

\input{04_overview} % Chương 1: Tổng quan

\input{05_basis} % Chương 2: Cơ sở lý thuyết

\input{06_experiment} % Chương 3: Thực nghiệm và đánh giá

\addcontentsline{toc}{chapter}{Tài liệu tham khảo}
\begin{thebibliography}{99}

\bibitem{jurafsky2023}
Daniel Jurafsky, James H. Martin.
\textit{Speech and Language Processing}. \\
Stanford University, 2023. \\
\url{https://web.stanford.edu/~jurafsky/slp3/4.pdf}

\bibitem{tokuc2024}
A.Aylin Tokuc, Michal Aibin. \\
\textit{How to improve Naïve Bayes Classification Performance}. 
Baeldung, 2024. \\
\url{https://www.baeldung.com/cs/naive-bayes-classification-performance}

\bibitem{vanderplas2017}
Jake VanderPlas. \\
\textit{Python Data Science Handbook}. 
O'Reilly Media, 2017. \\
\url{https://jakevdp.github.io/PythonDataScienceHandbook/}

\bibitem{wikipedia2024}
Wikipedia. \\
\textit{Xử lý ngôn ngữ tự nhiên}. 
Wikipedia, 2024. 
\url{https://vi.wikipedia.org/wiki/X%E1%BB%AD_l%C3%BD_ng%C3%B4n_ng%E1%BB%AF_t%E1%BB%B1_nhi%C3%AAn}

\bibitem{scikit2024}
Scikit-learn. \\
\textit{Multinomial Naive Bayes Classifier}. 
Scikit-learn, 2024. 
\url{https://scikit-learn.org/stable/modules/generated/sklearn.naive_bayes.MultinomialNB.html}

\bibitem{klein2011}
David Klein, Kyle Murray, Simon Weber. \\
\textit{Algorithmic Programming Language Identification}. 
arXiv, 2011. \\
\url{https://arxiv.org/abs/1106.4064}

\bibitem{jauhiainen2018}
Tommi Jauhiainen, Marco Lui, Marcos Zampieri, Timothy Baldwin, Krister Lindén. \\
\textit{Automatic Language Identification in Texts: A Survey}. 
arXiv, 2018. \\
\url{https://arxiv.org/abs/1804.08186}

\bibitem{raschka2014}
Sebastian Raschka. \\
\textit{Naive Bayes and Text Classification}. 
2014. \\
\url{https://sebastianraschka.com/Articles/2014_naive_bayes_1.html}

\bibitem{javapoint2024}
JavaPoint. \\
\textit{Machine Learning - Naive Bayes Classifier}. 
JavaPoint, 2024. \\
\url{https://www.javatpoint.com/machine-learning-naive-bayes-classifier}

\bibitem{sriram2022}
Sriram. \\
\textit{Multinomial Naive Bayes Explained: \\ 
Function, Advantages \& Disadvantages, Applications in 2024}. \\
Upgrad, 2022. \\
\url{https://www.upgrad.com/blog/multinomial-naive-bayes-explained/}

\end{thebibliography}

\end{document}